Title

### 2015-12-10 paper/paper.tex
explain kendall tau more

@@

To evaluate the pipeline as a whole, we used a revised Kendall's tau metric, in
accordance with \cite{lapata2006automatic}.

@@

>>>>

% TODO: comments about feature weights

@@

To evaluate the pipeline as a whole, we used a revised Kendall's tau metric, in
accordance with \cite{lapata2006automatic}. To score both the selection and
ordering simultaneously, we count the number of facts which are out of order.
This accounts for mistakes both in the subgraph selection, where a fact is
placed in the wrong set of facts, and in the subgraph ordering, where a group
of facts is placed in the wrong order.

@@

% TODO: comments about results
